Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
wordings

\item We provide experimental results showing that our fully automatic
program synthesis based approach is able to synthesise stable controllers
for a set of intricate benchmarks taken from the literature efficiently: the
median runtime for our benchmark set is $197$s, i.e., half of the
controllers can be synthesised in less than five minutes.

>>>>

\item We provide experimental results showing that our tool is able to
synthesise stable controllers for a set of intricate benchmarks taken from
the literature efficiently: the median runtime for our benchmark set is
$197$s, i.e., half of the controllers can be synthesised in less than five
minutes.
